\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-12-05 Proposal.tex
many changes regarding example

\newpage
\noindent
  With my signature, I certify that this thesis has been written by me
  using only the indicated resources and materials. Where I have
  presented data and results, the data and results are complete,
  genuine, and have been obtained by me unless otherwise acknowledged;
  where my results derive from computer programs, these computer
  programs have been written by me unless otherwise acknowledged. I
  further confirm that this thesis has not been submitted, either in
  part or as a whole, for any other academic degree at this or another
  institution.

@@

 \section*{Abstract}
 \label{sec:abstract}
Visualization of knowledge is important to foster learning. To optimize the visualization of information and its interdependencies, we will focus on identifying ways to present information without loosing context. The proposed research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics. This form of presenting knowledge should enable users to examine materials which they may have forgotten which form the basis for the understanding of the topics the audience is interested in.\\

Taking the typical lectures as an example, it is often the case that especially towards the end of the lecture students might have difficulties remembering earlier topics. When a new topic is introduced it would be ideal to have a simple way to find the dependencies and present students with an easy way to catch up.\\

The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, this research aims at visualizing the connections of different pieces of Mathematical concepts in a way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories. It will examine if and how spatial narrative and semantic closeness can be combined to foster learning. If this approach proves successful it will transform how we interact with course material and learning processes in general. Ultimately, this research may be applicable to almost all areas in which knowledge is supposed to be transferred.\\

@@

\begin{wrapfigure}{r}{0.5\textwidth}
  \vspace{-20pt}
  \begin{center}
                \fbox{\includegraphics[width=0.4\textwidth]{assets/Annie1}}
\end{center}
  \vspace{-20pt}
  \caption{Slide about the Pythagorean Theorem}
                \label{fig:Annie-presentation-teacher}
  \vspace{-10pt}
\end{wrapfigure}

To exemplify this: Annie, a young student learning Math, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}). She is given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is. This shows the dependencies of different pieces of information, i.e. the Pythagorean theorem depends on knowledge of squares, lengths, area calculation, angles, and right angles. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\

@@

The Oxford Dictionary of English \cite{OED:npentrel14} defines \textbf{information} as "what is conveyed or represented by a particular arrangement or sequence of things". Recalling figure \ref{fig:dataknow} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$}. For the term \textbf{Knowledge}, we will use the definition in Merriam-Webster \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association". \textbf{Association} is of special importance for the current project. We will define this as knowledge that is made up out of several pieces of information that are connected. In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used.\\

According to the Merriam-Webster dictionary \cite{Webster:npentrel14}, \textbf{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning". A Context can be easily explained with the example of Annie learning the Pythagorean theorem. The information about the calculation of the length of the third side of the triangle is only helpful for Annie within the context of the pieces of information this depends on, i.e. calculating squares, lengths, area calculation, angles, and right angles. This is the context that the Pythagorean theorem needs. We will be using the terms context and network almost interchangeably and depend on the reader to have the right intuition about these terms.\\

@@

@@

@@

@@

\subsection{Related Works}
\label{sec:relatedworks}

@@

Another piece of research has focused on the automatic generation of mind maps from text {Direct automatic generation of mind maps from text with M 2 Gen}. The software they developed uses Semantic Web technologies to create mind maps that show the relations between nodes that represent different objects. While this is close to what the proposed research intends in showing the relation between pieces of information, it does it on a word level. For instance, it can represent that Shakespeare lived in Stratford but it would not be able to show the dependencies of mathematical concepts as it is limited to representing nodes in single words within the mind map. We, on the other hand, will focus on exactly that, i.e. dependencies and the creation of interactive presentations.\\

>>>>

\newpage
\noindent
  With my signature, I certify that this thesis proposal has been written by me
  using only the indicated resources and materials. Where I have
  presented data and results, the data and results are complete,
  genuine, and have been obtained by me unless otherwise acknowledged;
  where my results derive from computer programs, these computer
  programs have been written by me unless otherwise acknowledged. I
  further confirm that this thesis has not been submitted, either in
  part or as a whole, for any other academic degree at this or another
  institution.

@@

 \section*{Abstract}
 \label{sec:abstract}
Visualization of knowledge is important to foster learning. To optimize the visualization of information and its interdependencies, we will focus on identifying ways to present information without loosing context. The proposed research aims at taking an existing annotated corpus and presenting its contents in an interactive way that allows the audience to see the dependencies of the covered topics. This form of presenting knowledge should enable users to interactively examine materials that are related to the topics the audience is interested in.\\

Taking the typical lectures as an example, it is often the case that, especially towards the end of the semester, students have difficulties remembering earlier topics. When a new topic is introduced it would be ideal to have a simple way to find the dependencies and present students with an easy way to catch up.\\

The OMDoc (Open Mathematical Documents) format \cite{Kohlhase:OMDoc1.2} is a content markup scheme for mathematical documents. Using OMDoc, this research aims at visualizing the connections of different pieces of mathematical concepts in an interactive way that allows students to learn the concepts the current topic depends on, should they need to refresh their memories. It will examine if and how spatial narrative and semantic closeness can be combined to foster learning. If this approach proves successful it will transform how we interact with course material and learning processes in general. Ultimately, this research may be applicable to almost all areas in which knowledge is supposed to be transferred.\\

@@

To exemplify this: Annie, a young student learning Math, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}). She is given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is. This shows the dependencies of different pieces of information (see figure \ref{fig:Annie-presentation-information}), i.e. the Pythagorean theorem depends on knowledge of squares,triangles, lengths, area calculation, and right angles. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\

\begin{figure}[H]
        \centering
        \begin{subfigure}[b]{0.45\textwidth}
                \fbox{\includegraphics[width=\textwidth]{assets/Annie1}}
			   \caption{Simple, explanatory slide}
                \label{fig:Annie-presentation-teacher}
        \end{subfigure}%
        \qquad %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.45\textwidth}
                \fbox{\includegraphics[width=\textwidth]{assets/Annie2}}
		  \caption{Information dependencies}
                \label{fig:Annie-presentation-information}
        \end{subfigure}
        \caption{Pythagorean Theorem}\label{fig:PythagoreanTheorem}
\end{figure}

@@

The Oxford Dictionary of English \cite{OED:npentrel14} defines \textbf{information} as "what is conveyed or represented by a particular arrangement or sequence of things". Recalling figure \ref{fig:PythagoreanTheorem} and our contrived story of Annie, an example for information is the sequence \textit{$a^2 + b^2 = c^2$} (see \ref{fig:Annie-presentation-teacher}). For the term \textbf{Knowledge}, we will use the definition in Merriam-Webster \cite{Webster:npentrel14} which defines it as the "fact or condition of knowing something with familiarity gained through experience or association". \textbf{Association} is of special importance for the current project. We will define this as knowledge that is made up out of several pieces of information that are connected. In the example from above knowledge would be knowing when and how the Pythagorean theorem can be used by knowing the information that the usage of the Pythagorean theorem depends on (see \ref{fig:Annie-presentation-information}).\\

\begin{wrapfigure}{r}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.45\textwidth]{assets/Annie3}
    }
  \end{center}
\vspace{-20pt}
  \caption{Information in context}
  \label{fig:Annie-context}
\vspace{-10pt}
\end{wrapfigure}

According to the Merriam-Webster dictionary \cite{Webster:npentrel14}, \textbf{context} is defined as "the parts of a discourse that surround a word or passage and can throw light on its meaning". Context can be easily explained with the example of Annie learning the Pythagorean theorem. The information about the calculation of the length of the third side of the triangle is only helpful for Annie within the context of the pieces of information this depends on, i.e. calculating squares, area calculation, triangles, and right angles. This is the context that the Pythagorean theorem needs. We will be using the terms context and network almost interchangeably and depend on the reader to have the right intuition about these terms.\\

@@

\begin{wrapfigure}{l}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.45\textwidth]{assets/Annie4xml}
    }
  \end{center}
\vspace{-20pt}
  \caption{Information in context}
  \label{fig:Annie-context}
\vspace{-10pt}
\end{wrapfigure}

@@

\ednote{on top of the info about when it appears within the course.}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.45\textwidth]{assets/Annie4ancient2}
    }
  \end{center}
\vspace{-20pt}
  \caption{Course-ancient information}
  \label{fig:Annie-context}
\vspace{-10pt}
\end{wrapfigure}

@@

\subsection{Related Work}
\label{sec:relatedworks}

@@

Another piece of research has focused on the automatic generation of mind maps from text \cite{abdeen2009direct}. The software they developed uses Semantic Web technologies to create mind maps that show the relations between nodes that represent different objects. While the proposed research also intends to show the relation between pieces of information, it does it on a different level. For instance, it can represent that Shakespeare lived in Stratford but it would not be able to show the dependencies of mathematical concepts as it is limited to representing nodes in single words within the mind map. We, on the other hand, will focus on exactly that, i.e. dependencies and the creation of interactive presentations.\\
